Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2015-11-30 Docs/IJES/journal.tex
minor changes
modifications in structure to accomplish ijes layout

\usepackage{natbib,stfloats}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{tabu}
\usepackage{listings}
\usepackage[table]{xcolor}
\usepackage{multirow}
\renewcommand{\lstlistingname}{Algorithm}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[scale=0.9]{figures/esbmc-arch-new.pdf} 
	\caption{ESBMC architecture.}
	\label{ESBMC-Architecture}
\end{figure}

@@

\vspace{2 mm}
\begin{lstlisting}[basicstyle=\footnotesize,label={lst:example}, language=C,numbers=left, numberstyle=\tiny, numbersep=7pt,frame=tb,captionpos=b, caption={OpenMP basic Example.}]
int k;
#pragma omp parallel for
for (k = 0; k < 10; k++)
  a[k] = 2*k;
\end{lstlisting}

In the above example, the {\it for} loop is executed in parallel. Each iteration of the loop is executed in a separated thread; and each thread may use an idle processor. There is also a way to specify critical regions, which is a code block that is guaranteed to be executed by a single thread at a time. To create a critical region, the ``\textit{\#pragma omp critical}'' directive is routinely used.

@@

\vspace{2.5 mm}
\begin{lstlisting}[basicstyle=\footnotesize,language=C,caption={OpenMP basic Example.},label={vZ},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
(Declare-Const K Int) 
(Declare-Const W Int)
(assert (< K 2)) 
(assert (< (- W K) 1))
(maximize (+ K W)) 
(check-sat)
\end{lstlisting}

Fig.~\ref{vZ-Architecture} shows the $\nu$Z architecture. Initially, the SMT formula with objectives is converted to $0-1$ constraints, which leads to a Pseudo-Boolean Optimization (PBO)~\cite{Barth1995,Vasco2005}. If there are many objective functions, $\nu$Z invokes OptSAT for arithmetic or MaxSAT for soft constraints. For constraints using real values, $\nu$Z combines linear arithmetic objectives and uses only one instance of OptSMT. When ``soft constrains'' is used in the mode `` lexicographic'', $\nu$Z invokes MaxSAT using multiple calls for its engine.

\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.21]{figures/vzArch.png} 
	\caption{$\nu$Z architecture extracted from~\cite{Bjorner2015}.}
	\label{vZ-Architecture}
\end{figure}

@@

\vspace{2 mm}
\begin{lstlisting}[basicstyle=\footnotesize,caption={Pseudocode describing sequential ESBMC.},label={Pseudocode-describing-ESBMC},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny,mathescape=true]
Initialize variables 
Declare number of nodes and edges
Declare hardware cost of each node as array (h)
Declare software cost of each node as array (s)
Declare communication cost of each edge (c)
Declare the initial sw cost of ($S_0$)
Declare transposed incidence matrix graph G(E)
Define the solutions ($X_i$) as Boolean
main {
 For TipH = 0 to Hmax Do {
  Populate $X_i$ with nondet / test values
  Calculate s(1-x)+c|Ex| and store at variable
  Requirement isued by Assume (variable <= $S_0$)
  Calculate Hp cost Based on value of $X_i$
  Violation check with Assert(Hp > TipH)
 }
}
\end{lstlisting}

It is possible to inform to ESBMC with which type of values the variables must be tested. Therefore, there is a declaration to populate all decision variables $x$ with non-deterministic Boolean values. Those values that change for each test will generate a possible solution and obey the constraints. If this is achieved, then a feasible solution is found and the ASSUME directive is responsible for ensuring the compliance of those constrains (\textit{i.e.}, $A.x \leq b$).

@@

\begin{figure}[h]
	\centering
  \includegraphics[scale=0.77]{figures/esbmc-ss.pdf} 
	\caption{ESBMC-SS approach.}
	\label{ESBMC-Multi-core}
\end{figure}

@@

\begin{figure}[h]
	\centering
  \includegraphics[scale=0.77]{figures/esbmc-ps.pdf} 
	\caption{ESBMC-PS approach.}
	\label{ESBMC-Multi-core-Optimized-Sequential-Approach}
\end{figure}

@@

\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.77]{figures/esbmc-pb.pdf} 
	\caption{ESBMC-PB approach.}
	\label{ESBMC-Binary-Approach}
\end{figure}

@@

\begin{figure}[h!]
	\centering
  \includegraphics[scale=0.17]{figures/Fig4.png}
	\caption{Binary step calculation.}
	\label{Binary-Step-Calculation}
\end{figure}

@@

\vspace {2 mm}
\begin{lstlisting}[basicstyle=\footnotesize,caption={Steps calculation using intervals.},label={Steps-Calculation-using-Intervals},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
GetNextStep(){
 int largestChunk = -1;
 chunk largest;
 for each(chunk in chunks){
  if(chunk.right - chunk.left > largestChunk){
    largestChunk = chunk.right - chunk.left;
    largest = chunk;
  }
 }	
 chunks.remove(largest);	
 int median = largest.left + 
   floor((largest.right - largest.left) / 2);
 if(median > 0){
  if(largest.right - largest.left > 1)
   chunks.add(
     new chunk(largest.left, median - 1)
   );	
  if(largest.right != largest.left)
   chunks.add(
    new chunk(median + 1, largest.right)
   );
 }
 return median;
}
\end{lstlisting}

Algorithm~\ref{worker-sample} describes how the worker starts and monitors ESBMC instances. The algorithm starts by retrieving the step to be executed from the controller (line $1$), then initiates the ESBMC instance and obtains the process \textit{id} from the forked process (line $2$). While the step is being executed, the controller checks whether this step is still needed (line $4$). If not, then the ESBMC instance is killed (line $5$) and the worker is free to initiate another step.

\vspace {2 mm}
\begin{lstlisting}[basicstyle=\footnotesize,caption={Worker sample.},label={worker-sample},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
step = controller.GetNextStep();
int pid = ExecuteStep(step);
while(isRunning(pid)){
 if(!controller.isNeeded(step))
   kill(pid);
}
\end{lstlisting}

@@

\vspace {2 mm}
\begin{lstlisting}[basicstyle=\footnotesize,caption={Pseudocode describing ESBMC-$\nu$Z.},label={vZ-pseudocode},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny,mathescape=true]
-Initialize Variables
 Create vZ context 
 Create binary vector (x)
 Declare number of nodes, edges and $S_0$
 Declare hardware cost of each node as array (h) 
 Declare software cost of each node as array (s)
 Declare communication cost of each edge (c)
 Declare transposed incidence matrix graph G(E)
-Arithmetic Expressions
 SC = s(1-x)
 CMC = c*|EX|
 Fobj =  x[i] * h[i]
-Assert Constraints
 Add constraints (SF + CMC <= $S_0$)
 Add constraints to minimize Fobj
 Check Model
 Print Result
\end{lstlisting}

@@

\hspace{-5 mm}
\begin{minipage}{\linewidth}
\centering
\small
\sffamily\small
\tabulinesep=4pt
\captionof{table}{Description of Benchmarks.} 
\begin{tabular}[c]{m{1.5cm}m{0.7cm}m{0.7cm}m{4.0 cm}}
\toprule[1.5pt]
\textbf{Name} & \textbf{Nodes} & \textbf{Edges} & \textbf{Description}\\
\midrule
\verb|CRC32| & \verb|25| & \verb|32| & \rmfamily 32-bit cyclic redundancy check ~\cite{Guthaus2001}\\
\hline
\verb|Patricia| & \verb|21| & \verb|48| & \rmfamily
\vspace{0.8 mm} Routine to insert values in Patricia Tree \cite{Guthaus2001}\\
\hline
\verb|Dijkstra| & \verb|26| & \verb|69| & \rmfamily \vspace{0.8 mm} Computer shortest paths in a graph ~\cite{Guthaus2001}\\
\hline
\verb|Clustering| & \verb|150| & \verb|331| & \rmfamily \vspace{0.8 mm} Image segmentation algorithm in a medical application\\
\hline
\verb|RC6| & \verb|329| & \verb|448| & \rmfamily \vspace{0.8 mm} RC6 cryptography graph algorithm\\
\hline
\verb|Fuzzy| & \verb|261| & \verb|422| & \rmfamily \vspace{0.8 mm} Clustering algorithm based on fuzzy logic\\
\hline
\verb|Mars| & \verb|417| & \verb|600| & \rmfamily 
\vspace{1 mm} MARS cipher from IBM algorithm\\
\bottomrule[1.5pt]
\label{tab:Description-of-Benchmarks} 
\end{tabular}\par
\bigskip
\end{minipage}

@@

\multirow{4}{*}{\textbf{\normalsize{Solution}}}
& & & & & & & & & \\
&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241} &  \normalsize{692} &  \normalsize{13820}   &  \normalsize{876} \\
&  \normalsize{Sp}   &  \normalsize{19}   &  \normalsize{4}   &  \normalsize{19}   &  \normalsize{46}   &  \normalsize{533}    &  \normalsize{4231}   &  \normalsize{297}  \\
& & & & & & & & & \\

@@

>>>>

\usepackage{natbib,stfloats}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage[labelsep=quad,font=small,justification=justified,singlelinecheck=false,format=plain,labelfont=bf,up,textfont=normal,up]{caption}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{tabu}
\usepackage{listings}
\usepackage[table]{xcolor}
\usepackage[tableposition=top]{caption}
\usepackage{multirow}
\renewcommand{\lstlistingname}{Figure}
\renewcommand{\figurename}{Figure}

\makeatletter
\AtBeginDocument{%
  \let\c@figure\c@lstlisting
  \let\thefigure\thelstlisting
  \let\ftype@lstlisting\ftype@figure % give the floats the same precedence
}
\makeatother

@@

\begin{figure}[ht]
	\caption{ESBMC architecture.}
	\centering
	\includegraphics[scale=0.9]{figures/esbmc-arch-new.pdf} 
	\label{ESBMC-Architecture}
\end{figure}

@@

\begin{lstlisting}[basicstyle=\footnotesize,label={lst:example}, language=C, numberstyle=\tiny, numbersep=7pt,frame=tb,captionpos=t, caption={OpenMP basic Example.}]
int k;
#pragma omp parallel for
for (k = 0; k < 10; k++)
  a[k] = 2*k;
\end{lstlisting}

\vspace{2 mm}
In the above example, the {\it for} loop is executed in parallel. Each iteration of the loop is executed in a separated thread; and each thread may use an idle processor. There is also a way to specify critical regions, which is a code block that is guaranteed to be executed by a single thread at a time. To create a critical region, the ``\textit{\#pragma omp critical}'' directive is routinely used.

@@

\begin{lstlisting}[basicstyle=\footnotesize,language=C,caption={OpenMP basic Example.},label={vZ},numbersep=7pt,frame=tb,captionpos=t,numberstyle=\tiny]
(Declare-Const K Int) 
(Declare-Const W Int)
(assert (< K 2)) 
(assert (< (- W K) 1))
(maximize (+ K W)) 
(check-sat)
\end{lstlisting}

\vspace{2 mm}
Fig.~\ref{vZ-Architecture} shows the $\nu$Z architecture. Initially, the SMT formula with objectives is converted to $0-1$ constraints, which leads to a Pseudo-Boolean Optimization (PBO)~\cite{Barth1995,Vasco2005}. If there are many objective functions, $\nu$Z invokes OptSAT for arithmetic or MaxSAT for soft constraints. For constraints using real values, $\nu$Z combines linear arithmetic objectives and uses only one instance of OptSMT. When ``soft constrains'' is used in the mode `` lexicographic'', $\nu$Z invokes MaxSAT using multiple calls for its engine.

\begin{figure}[ht]
	\caption{$\nu$Z architecture extracted from~\cite{Bjorner2015}.}
	\centering
	\includegraphics[scale=0.21]{figures/vzArch.png} 
	\label{vZ-Architecture}
\end{figure}

@@

\begin{lstlisting}[basicstyle=\footnotesize,caption={Pseudocode describing sequential ESBMC.},label={Pseudocode-describing-ESBMC},numbersep=7pt,frame=tb,captionpos=t,numberstyle=\tiny,mathescape=true]
Initialize variables 
Declare number of nodes and edges
Declare hardware cost of each node as array (h)
Declare software cost of each node as array (s)
Declare communication cost of each edge (c)
Declare the initial sw cost of ($S_0$)
Declare transposed incidence matrix graph G(E)
Define the solutions ($X_i$) as Boolean
main {
 For TipH = 0 to Hmax Do {
  Populate $X_i$ with nondet / test values
  Calculate s(1-x)+c|Ex| and store at variable
  Requirement isued by Assume (variable <= $S_0$)
  Calculate Hp cost Based on value of $X_i$
  Violation check with Assert(Hp > TipH)
 }
}
\end{lstlisting}

\vspace{2 mm}
It is possible to inform to ESBMC with which type of values the variables must be tested. Therefore, there is a declaration to populate all decision variables $x$ with non-deterministic Boolean values. Those values that change for each test will generate a possible solution and obey the constraints. If this is achieved, then a feasible solution is found and the ASSUME directive is responsible for ensuring the compliance of those constrains (\textit{i.e.}, $A.x \leq b$).

@@

\begin{figure}[h]
	\caption{ESBMC-SS approach.}
	\centering
	\includegraphics[scale=0.77]{figures/esbmc-ss.pdf} 	
	\label{ESBMC-Multi-core}
\end{figure}

@@

\begin{figure}[h]
	\caption{ESBMC-PS approach.}
	\centering
	\includegraphics[scale=0.77]{figures/esbmc-ps.pdf} 	
	\label{ESBMC-Multi-core-Optimized-Sequential-Approach}
\end{figure}

@@

\begin{figure}[ht]
	\caption{ESBMC-PB approach.}
	\centering
	\includegraphics[scale=0.77]{figures/esbmc-pb.pdf} 
	\label{ESBMC-Binary-Approach}
\end{figure}

@@

\begin{figure}[h!]
	\caption{Binary step calculation.}
	\centering
	\includegraphics[scale=0.17]{figures/Fig4.png}	
	\label{Binary-Step-Calculation}
\end{figure}

@@

\begin{lstlisting}[basicstyle=\footnotesize,caption={Steps calculation using intervals.},label={Steps-Calculation-using-Intervals},numbersep=7pt,frame=tb,captionpos=t,numberstyle=\tiny]
GetNextStep(){
 int largestChunk = -1;
 chunk largest;
 for each(chunk in chunks){
  if(chunk.right - chunk.left > largestChunk){
    largestChunk = chunk.right - chunk.left;
    largest = chunk;
  }
 }	
 chunks.remove(largest);	
 int median = largest.left + 
   floor((largest.right - largest.left) / 2);
 if(median > 0){
  if(largest.right - largest.left > 1)
   chunks.add(
     new chunk(largest.left, median - 1)
   );	
  if(largest.right != largest.left)
   chunks.add(
    new chunk(median + 1, largest.right)
   );
 }
 return median;
}
\end{lstlisting}

\vspace {2 mm}
Algorithm~\ref{worker-sample} describes how the worker starts and monitors ESBMC instances. The algorithm starts by retrieving the step to be executed from the controller (line $1$), then initiates the ESBMC instance and obtains the process \textit{id} from the forked process (line $2$). While the step is being executed, the controller checks whether this step is still needed (line $4$). If not, then the ESBMC instance is killed (line $5$) and the worker is free to initiate another step.

\begin{lstlisting}[basicstyle=\footnotesize,caption={Worker sample.},label={worker-sample},numbersep=7pt,frame=tb,captionpos=t,numberstyle=\tiny]
step = controller.GetNextStep();
int pid = ExecuteStep(step);
while(isRunning(pid)){
 if(!controller.isNeeded(step))
   kill(pid);
}
\end{lstlisting}

@@

\begin{lstlisting}[basicstyle=\footnotesize,caption={Pseudocode describing ESBMC-$\nu$Z.},label={vZ-pseudocode},numbersep=7pt,frame=tb,captionpos=t,numberstyle=\tiny,mathescape=true]
-Initialize Variables
 Create vZ context 
 Create binary vector (x)
 Declare number of nodes, edges and $S_0$
 Declare hardware cost of each node as array (h) 
 Declare software cost of each node as array (s)
 Declare communication cost of each edge (c)
 Declare transposed incidence matrix graph G(E)
-Arithmetic Expressions
 SC = s(1-x)
 CMC = c*|EX|
 Fobj =  x[i] * h[i]
-Assert Constraints
 Add constraints (SF + CMC <= $S_0$)
 Add constraints to minimize Fobj
 Check Model
 Print Result
\end{lstlisting}

@@

\vspace{5 mm}
\hspace{-5 mm}
\begin{minipage}{\linewidth}
\centering
\small
\sffamily\small
\tabulinesep=4pt
\captionof{table}{Description of Benchmarks.} 
\begin{tabular}[c]{m{1.5cm}m{0.7cm}m{0.7cm}m{4.0 cm}}
\toprule[1.5pt]
\textbf{Name} & \textbf{Nodes} & \textbf{Edges} & \textbf{Description}\\
\midrule
\verb|CRC32| & \verb|25| & \verb|32| & \rmfamily 32-bit cyclic redundancy check ~\cite{Guthaus2001}\\
\hline
\verb|Patricia| & \verb|21| & \verb|48| & \rmfamily
\vspace{0.8 mm} Routine to insert values in Patricia Tree \cite{Guthaus2001}\\
\hline
\verb|Dijkstra| & \verb|26| & \verb|69| & \rmfamily \vspace{0.8 mm} Computer shortest paths in a graph ~\cite{Guthaus2001}\\
\hline
\verb|Clustering| & \verb|150| & \verb|331| & \rmfamily \vspace{0.8 mm} Image segmentation algorithm in a medical application\\
\hline
\verb|RC6| & \verb|329| & \verb|448| & \rmfamily \vspace{0.8 mm} RC6 cryptography graph algorithm\\
\hline
\verb|Fuzzy| & \verb|261| & \verb|422| & \rmfamily \vspace{0.8 mm} Clustering algorithm based on fuzzy logic\\
\hline
\verb|Mars| & \verb|417| & \verb|600| & \rmfamily 
\vspace{1 mm} MARS cipher from IBM algorithm\\
\bottomrule[1.5pt]
\label{tab:Description-of-Benchmarks} 
\end{tabular}\par
\bigskip
\end{minipage}

@@

\multirow{4}{*}{\textbf{\normalsize{Exact Solution}}}
& & & & & & & & & \\
&  \normalsize{Hp}   &  \normalsize{15}   &  \normalsize{47}   &  \normalsize{31}   &  \normalsize{241} &  \normalsize{692} &  \normalsize{13820}   &  \normalsize{876} \\
&  \normalsize{Sp}   &  \normalsize{19}   &  \normalsize{4}   &  \normalsize{19}   &  \normalsize{46}   &  \normalsize{533}    &  \normalsize{4231}   &  \normalsize{297}  \\
& & & & & & & & & \\

@@

\bibitem[\protect\citeauthoryear{Holzmann}{2012}]{Holzmann2012}
Holzmann, G. (2012) 'Parallelizing the spin model checker', {\it Proc. of the Intl. Symp. on Model Checking Software}, Vol. 7385, pp.155--171
